---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# themeparks

<!-- badges: start -->
[![R-CMD-check](https://github.com/r4fun/themeparks/workflows/R-CMD-check/badge.svg)](https://github.com/r4fun/themeparks/actions)
<!-- badges: end -->

The goal of themeparks is to provide an R interface to some of the functionality found at [`cubehouse/themeparks`](https://github.com/cubehouse/themeparks). Currently, only `r length(themeparks::parks())` of the 62 parks are supported here.

## Installation

You can install the development version of themeparks with:

``` r
# install.packages("devtools")
devtools::install_github("tylurp/themeparks")

```

## Example

Get park information and wait times:

```{r example}
library(themeparks)

parks()

park_info("WaltDisneyWorldMagicKingdom")

park_wait_times("WaltDisneyWorldMagicKingdom")

park_calendar("WaltDisneyWorldMagicKingdom")
```

## Related work

* [`LucyMcGowan/parkhoppr`](https://github.com/LucyMcGowan/parkhoppr)

## Acknowledgments

* [`cubehouse/themeparks`](https://github.com/cubehouse/themeparks)
